---
title: "Plot Functions"
author: "Rajesh Rajendran"
date: '2022-06-03'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Introduction
- This application is very user friendly GUI for displaying the commonly used 
distributions
- The application plot's histograms of the distributions.
- This is very useful for high-school and under graduate students who takes  
first class in statistics and probability distributions.
- The app allows to choose the number of points to be simulated for the selected distribution. 

## Distributions
The application creates the histogram for following distributions

- Normal Distribution
- Uniform Distribution
- Log Normal Distribution
- Exponential Distribution

## Example Normal Distribution
The app draws the histogram as in figure below. It is histogram of 1000 samples from random normal distribution function.

```{r cars, echo = TRUE}
hist(rnorm(1000), probability = TRUE)
```

## Conclusion

- It is a fun application which allows students to play around with distribution
in interactive way.
- More distributions are to be added in future.
